\LARGE \bf The TransHumUs project for the French Pavilion \\ at La Biennale di Venezia 2015

### 2015-08-31 docs/article.tex
fig_ok

\begin{figure}[thpb]
    \centering
    \begin{tikzpicture}
        \draw [->] (-3, 0) -- (3, 0);
        \draw [->] (0, -3) -- (0, 3);
        \coordinate (o) at (0,0);
        \coordinate (v) at (0.5, {sqrt(3) / 2});
        \coordinate (x) at ({+sqrt(2) / 2}, {sqrt(2) / 2});
        \coordinate (y) at ({-sqrt(2) / 2}, {sqrt(2) / 2});
        \coordinate (z) at (0, -1);
        \draw (o) node [draw,thick,minimum size=4cm,name=O,regular polygon,regular polygon sides=8] {};
        \draw (O) node [fill=green,circle,draw,inner sep=1pt] {};
        \coordinate (a) at (O.side 6);
        \coordinate (b) at (O.side 8);
        \coordinate (c) at (O.side 3);
        \coordinate (d) at ($ (O.side 7) + (0, 0.5) $);
        \draw (a) node [fill=red,circle,draw,inner sep=1pt] {};
        \draw (b) node [fill=red,circle,draw,inner sep=1pt] {};
        \draw (c) node [fill=red,circle,draw,inner sep=1pt] {};
        \draw [->, red] (o) -- (v) node [left] {$v$};
        \draw [->, red] (a) -- ++(v) node [left] {$v$};
        \draw [->, red] (b) -- ++(v) node [right] {$v$};
        \draw [->, red] (c) -- ++(v) node [left] {$v$};
        \draw [->, blue] (a) -- ++(x) node [right] {$\omega R_1$};
        \draw [->, blue] (b) -- ++(y) node [left] {$\omega R_2$};
        \draw [->, blue] (c) -- ++(z) node [left] {$\omega R_3$};
        \draw [->] (a) -- ($ (a) + (v) + (x) $) node [left] {$v_1$};
        \draw [->] (b) -- ($ (b) + (v) + (y) $) node [left] {$v_2$};
        \draw [->] (c) -- ($ (c) + (v) + (z) $) node [below] {$v_3$};
        \draw [blue, dashed] ($ (a) + (v) $) -- ($ (a) + (v) + (x) $);
        \draw [blue, dashed] ($ (b) + (v) $) -- ($ (b) + (v) + (y) $);
        \draw [blue, dashed] ($ (c) + (v) $) -- ($ (c) + (v) + (z) $);
        \draw [red, dashed] ($ (a) + (x) $) -- ($ (a) + (v) + (x) $);
        \draw [red, dashed] ($ (b) + (y) $) -- ($ (b) + (v) + (y) $);
        \draw [red, dashed] ($ (c) + (z) $) -- ($ (c) + (v) + (z) $);
        \draw [blue] (o) -- (a) node [pos=0.5, above] {$R_1$};
        \draw [blue] (o) -- (b) node [pos=0.7, below] {$R_2$};
        \draw [blue] (o) -- (c) node [pos=0.5, above] {$R_3$};
        \pic [black!60!green, draw, ->, "$\theta$", angle eccentricity=1.5] {angle = d--o--v};
        \pic [blue, draw, ->, "$\omega$", angle eccentricity=1.1, angle radius=75] {angle = d--o--b};
    \end{tikzpicture}
    \caption{$(v_i, \theta_i)$ as a function of $(v, \theta, \omega)$}
    \label{octogon}
\end{figure}

>>>>

\begin{figure}[thpb]
    \centering

    \begin{tikzpicture}
        \draw [->] (-3, 0) -- (3, 0);
        \draw [->] (0, -3) -- (0, 3);
        \coordinate (o) at (0, 0);
        \coordinate (v) at (0.5, {sqrt(3) / 2});
        \coordinate (x) at ({+sqrt(2) / 2}, {sqrt(2) / 2});
        \coordinate (y) at ({-sqrt(2) / 2}, {sqrt(2) / 2});
        \coordinate (z) at (0, -1);
        \draw (o) node [draw, thick, minimum size=4cm, name=O, regular polygon, regular polygon sides=8] {};
        \draw (O) node [fill=green, circle, draw, inner sep=1pt] {};
        \coordinate (a) at (O.side 6);
        \coordinate (b) at (O.side 8);
        \coordinate (c) at (O.side 3);
        \coordinate (d) at (O.side 7);
        \coordinate (e) at ($ (d) + (0, 0.5) $);
        \coordinate (f) at ($ (a) + (1, 0) $);
        \coordinate (g) at ($ (b) + (1, 0) $);
        \coordinate (h) at ($ (c) + (1, 0) $);
        \coordinate (i) at ($ (a) + (v) + (x) $);
        \coordinate (j) at ($ (b) + (v) + (y) $);
        \coordinate (k) at ($ (c) + (v) + (z) $);
        \draw (a) node [fill=red, circle, draw, inner sep=1pt] {};
        \draw (b) node [fill=red, circle, draw, inner sep=1pt] {};
        \draw (c) node [fill=red, circle, draw, inner sep=1pt] {};
        \draw [->, red] (o) -- (v) node [left] {$v$};
        \draw [->, red] (a) -- ++(v) node [left] {$v$};
        \draw [->, red] (b) -- ++(v) node [right] {$v$};
        \draw [->, red] (c) -- ++(v) node [left] {$v$};
        \draw [->, blue] (a) -- ++(x) node [right] {$\omega R_1$};
        \draw [->, blue] (b) -- ++(y) node [left] {$\omega R_2$};
        \draw [->, blue] (c) -- ++(z) node [left] {$\omega R_3$};
        \draw [->] (a) -- (i) node [left] {$v_1$};
        \draw [->] (b) -- (j) node [left] {$v_2$};
        \draw [->] (c) -- (k) node [below] {$v_3$};
        \draw [blue, dashed] ($ (a) + (v) $) -- (i);
        \draw [blue, dashed] ($ (b) + (v) $) -- (j);
        \draw [blue, dashed] ($ (c) + (v) $) -- (k);
        \draw [red, dashed] ($ (a) + (x) $) -- (i);
        \draw [red, dashed] ($ (b) + (y) $) -- (j);
        \draw [red, dashed] ($ (c) + (z) $) -- (k);
        \draw [blue] (o) -- (a) node [pos=0.5, above] {$R_1$};
        \draw [blue] (o) -- (b) node [pos=0.7, below] {$R_2$};
        \draw [blue] (o) -- (c) node [pos=0.5, above] {$R_3$};
        \pic [black!60!green, draw, ->, "$\theta$", angle eccentricity=1.5] {angle = d--o--v};
        \pic [blue, draw, ->, "$\omega$", angle eccentricity=1.1, angle radius=80] {angle = e--o--b};
        \pic [draw, ->, "$\theta_1$", angle radius=20, angle eccentricity=1.3] {angle = f--a--i};
        \pic [draw, ->, "$\theta_2$", angle radius=10, angle eccentricity=1.5] {angle = g--b--j};
        \pic [draw, ->, "$\theta_3$", angle radius=5, angle eccentricity=2] {angle = h--c--k};
    \end{tikzpicture}

    \caption{$(v_i, \theta_i)$ as a function of $(v, \theta, \omega)$}
    \label{octogon}
\end{figure}
